\section{Conclusion}
\label{section:conclusion}

In this paper, we proposed an approach to rapidly model and evaluate transportation and power system scenarios. 
%For this, we extended an existing approach to transportation system modeling and scenario exploration to include a suitable representation of the power system. 
The proposed holistic and component-based approach is able to model power systems with detailed electric devices as well as transportation systems with individual cars microscopically. Our approach allows to rapidly explore and vary configurations of transportation system and electric network scenarios. We evaluated several incremental scenarios varying in stage of expansion of renewable and smart energy devices as well as focus of system objectives. 
%the weight of objectives of transportation and power systems. 
Scenario results demonstrated the feasibility of the modeling technique and rapid evaluation of multiple scenarios. However, key issues which have to be addressed are the validity and applicability the approach.
Future work includes refinement of model accuracy through vehicle model improvements and utilization as well as modeling of additional objectives and systems. Furthermore, modeling representative traffic infrastructures with OpenStreetMap and validation of results obtained with our approach represent major next steps. Finally, to be able to handle larger problem scales, more detailed models and resulting computational complexity, we currently work on effective behavior estimation algorithms.
